---
title: "Getting Started with scratchr"
author: "VP Nagraj"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Introduction

**scratchr** is a package ... a real *R* package ... with all kinds of not-so-useful functions built-in. To get started, try running `browseVignettes(package = "scratchr")` 
... and you're back here!

## `hello()`

One of two functions that ships with **scratchr**, `hello()` will say hello. It also features very important ASCII illustrations of animals, creatures, star wars characters, etc courtesy of the **cowsay** package. It takes two arguments: 

- *name*: what you would like the program to call you
- *animal*: what kind of critter you would like displayed

```{r}
library(scratchr)
hello(name = "vp", animal = "spider")
```

**nb** if you leave animal blank, you'll get a random creature ... and if you leave name blank, you'll be a "user"

```{r}
hello()
```

## `bday_clock()`

Ever wonder how many days until your birthday?

```{r}
bday_clock(month = "January", day = 1)
```

## `futurepop`

**scratchr** also includes a built-in time series dataset. This data is a combination of the `uspop` data (see `?datasets::uspop`) and some completely arbitrary population projections that run through 2030.

```{r}
futurepop
str(futurepop)
```

It seems that the population is increasing ...

```{r}
plot(futurepop)
```


